### 2018-09-10 methods.tex
@katyhuff comments implemented

Saltproc datasets are time-series, meaning that every value is recorded every 
timestep. The datasets SaltProc produces are listed below,
where the values inside the parenthesis are the dataset sizes:

>>>>

SaltProc records every value every timestep. The resulting time series datasets 
produced by SaltProc are listed below are listed below,
where the values inside the parenthesis are the dataset sizes:

### 2018-09-10 results.tex
maybe all changes handled
Mark's edits implemented #27
@katyhuff comments implemented

\subsection{Neutron flux}
Figure~\ref{fig:radial_flux} shows the radial distribution of fast and thermal 
neutron flux for the both initial and equilibrium composition. The neutron fluxes
have similar shapes for both compositions but the equilibrium case has a harder 
spectrum. A significant spectral shift was observed in the central region of 
the core (zone I), while for the outer region (zone II), it is negligible for fast 
but notable for thermal neutrons. These neutron flux radial distributions 
agree with the fluxes in the original ORNL report \cite{robertson_conceptual_1971}. 
Overall, spectrum hardening during \gls{MSBR} operation should be carefully 
studied when designing the reactivity control system.
\begin{figure}[ht!] % replace 't' with 'b' to force it to \centering
  \includegraphics[width=\textwidth]{radial_flux.png} \caption{Radial neutron 
  flux distribution for initial and equilibrium fuel salt composition.}
  \label{fig:radial_flux}
\end{figure}

@@

generated in zone I and the majority of $^{233}$Th is 

@@

coefficient of 1.3$\times10^{-6}$1/K \cite{robertson_conceptual_1971}. A new 

@@

\subsection{Six Factor Analysis}
The effective multiplication factor can be expressed using next formula:
\begin{align*}
k_{eff} = k_{inf} P_f  P_t = \eta \epsilon p f P_f P_t
\end{align*}

>>>>

\subsection{Neutron flux}
Figure~\ref{fig:radial_flux} shows the radial distribution of fast and thermal 
neutron flux for the both initial and equilibrium composition. The neutron fluxes
have similar shapes for both compositions but the equilibrium case has a harder 
spectrum. A significant spectral shift was observed in the central region of 
the core (zone I), while for the outer region (zone II), it is negligible for fast 
but notable for thermal neutrons. These neutron flux radial distributions are in 
good agreement with original ORNL report \cite{robertson_conceptual_1971}. 
Overall, spectrum hardening during \gls{MSBR} operation should be carefully 
studied when designing the reactivity control system.
\begin{figure}[ht!] % replace 't' with 'b' to force it to \centering
  \includegraphics[width=\textwidth]{radial_flux.png} \caption{Radial neutron 
  flux distribution for initial and equilibrium fuel salt composition.}
  \label{fig:radial_flux}
\end{figure}

@@

generated in zone I except the majority of $^{233}$Th that is 

@@

coefficient of 1.3$\times10^{-6}$K$^{-1}$ \cite{robertson_conceptual_1971}. A new 

@@

\subsection{Six Factor Analysis}
The effective multiplication factor can be expressed using the following formula:
\begin{align*}
k_{eff} = k_{inf} P_f  P_t = \eta \epsilon p f P_f P_t
\end{align*}
